If the Null Fits, You Must Omit: Measurement Artifacts Undermine Group Polarization Replications

### 2025-11-18 GroupPolarizationStatmod/paper/method.tex
drafting method cont'd

\input{method-tables.tex}

@@

Formally, the probability density function is
\begin{equation}
  f(\omega) = 
    \frac{1}{\sigma \sqrt{2 \pi}} e^{-\frac{(\omega - \mu)^2}{2 \sigma^2}}.
  \label{eq:normal_pdf}
\end{equation}
\noindent
Assume there are $B$ bins, meaning there are $B+1$ \emph{thresholds} that
define which latent opinions get mapped to which bin values. The bin value,
$b_i$, is the numerical value of the $i$th bin.

@@

>>>>

\begin{center}
\vspace{1.5em}
[ TABLE \ref{tab:latent-variables} ABOUT HERE ]
\vspace{1.5em}
\end{center}

@@

Formally, the probability density function is
\begin{equation}
  f(\omega) = 
    \frac{1}{\sigma \sqrt{2 \pi}} e^{-\frac{(\omega - \mu)^2}{2 \sigma^2}}.
  \label{eq:normal_pdf}
\end{equation}
\noindent
To set up our measurement simulation, we will represent
oridnal bin values as $b_i$ with $i=1,\ldots,B$—i.e., there are $B$ bins. 
To create $B$ bins there must be $B+1$ \emph{thresholds} that define what
range of latent opinions correspond to which ordinal bin value.

\begin{center}
  \vspace{1.5em}
  [ TABLE \ref{tab:experiment-parameters} ABOUT HERE ]
  \vspace{1.5em}
\end{center}

All bins have a width of 1 in latent opinion space, except for the two most
extreme bins at opposite ends of the sentiment spectrum—this works because
bin values are always separated by 1. All continuous latent opinion values
$\omega < b_1 + \frac{1}{2} = \theta_1$ get mapped to the ordinal measurement
value $b_1$—so, $b_1$'s lower threshold is $\theta_0 = -\infty$.  Similarly,
all opinions $\omega > b_B - 0.5 = \theta_B$ are reported as the maximum bin
value, $b_B$, with an effective upper bound of $\theta_{B+1} = +\infty$.  We
can define all thresholds compactly as \cite{Liddell2018}
\begin{equation}
\theta_j = \begin{cases}
  -\infty         & \text{ if } j=0 \\
  \infty          & \text{ if } j=B \\
  b_1 + \frac{j + 1}{2} & \text{ otherwise.}
\end{cases}
\label{eq:thresholds}
\end{equation}
\noindent

We model the measurement of ordinal opinions by calculating the probability
density function over bins, written
\begin{equation}
  f[b_i] = \int_{\theta_{i - 1}}^{\theta_i} f(\omega) d\omega~,
  \label{eq:measurement-math}
\end{equation}
\noindent
switching to square brackets for the argument to $f$ now to emphasize that 
bins are discrete. With this ordinal measurement model we can caluclate the 
mean opinion of the simulated measurements like so
\begin{equation}
  \bar{o}_t = \frac{1}{B} \sum_{b=b_1}^{b_B} b \cdot f_t[b].
\end{equation}
\noindent

\begin{center}
\vspace{1.5em}
[ FIGURE \ref{fig:distros} ABOUT HERE ]
\vspace{1.5em}
\end{center}

Group polarization is the difference between the post-deliberation mean
observed opinion and the pre-deliberation one, 
which we can write as 
\begin{equation}
  g = \bar{o}_\mathrm{post} - \bar{o}_\mathrm{pre}.
  \label{eq:group-polarization}
\end{equation}
\noindent

\begin{center}
\vspace{1.5em}
[ TABLE \ref{tab:simulated-observations} ABOUT HERE ]
\vspace{1.5em}
\end{center}

@@

To analyze published replications we need to expand our notation to index
individual \emph{experiments} with replications, and from which 
different journal articles, track and analyze it,
